Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
Comment

A~\emph{ground set} is a group of nodes that repeatedly communicate if they are not collocated.
If an algorithm splits any pair of nodes from a ground set, then the adversary continues to produce requests to this pair until the algorithm collocates it.
Any competitive algorithm must maintain a~perfect partition of ground sets into clusters.
We emphasize that ground sets are revealed only upon their nodes are split.
The adversary constructs ground sets depending on the choices of a deterministic online algorithm.
Once we construct a ground set, it lasts until the end of the input sequence.
We say that a ground set is \emph{singleton} if it contains exactly one node.
We say that the node that belongs to a singleton ground set is \emph{isolated}.

>>>>

A~\emph{ground set} is a group of nodes that repeatedly communicate if they are not collocated.
If an algorithm splits any pair of nodes from a ground set, then the adversary continues to produce requests to this pair until the algorithm collocates it \maciek{learning model: does not need to continue issuing requests.}
Any competitive algorithm must maintain a~perfect partition of ground sets into clusters.
We emphasize that ground sets are revealed only upon their nodes are split.
The adversary constructs ground sets depending on the choices of a deterministic online algorithm.
Once we construct a ground set, it lasts until the end of the input sequence.
We say that a ground set is \emph{singleton} if it contains exactly one node.
We say that the node that belongs to a singleton ground set is \emph{isolated}.
